\acknowledgments{% \vskip2pc
  % {\narrower\noindent
  I would like to thank my advisor Dr. Faisal Hossain for his encouragement and guidance during the past three years. I benefit so much from his passion and insight of research. I have enjoyed the years working with him, and I especially appreciate his patience to allow me to freely explore various interesting questions before sitting down with the current topic of this dissertation.
  
  I would like to thank my committee members Dr. Erkan Istanbulluoglu, Dr. Ruby Leung, and my two graduate school representatives, Dr. Joseph Cook, and Dr. Daehyun Kim for their invaluable feedback and suggestions along with my research. I want to also thank Dr. Cliff Mass, for bringing the new perspective to and sharing climate projections in my study.
  
  I want to also thank the members at the SASWE group. It has been a pleasure working with you, and you have been giving great suggestions on my research from time to time.
   
  %I am grateful to the friends I have met since I came to Seattle in 2011. Especially, I would like to thank Ted Bohn, Ben Livneh, Shrad Shukla, Mu Xiao
  
  Thank you to my family for their incredible support throughout my graduate studies, especially during my most difficult time. This dissertation cannot be completed without your support.
  
  At the time of writing, Chapter \ref{ch:JHE} has been published as \textit{Chen et al.} [2017] in the \textit{Journal of Hydrologic Engineering}, and Chapter \ref{ch:EF} has been published as \textit{Chen and Hossain} [2016] in the \textit{Earth's Future}. I would like to thank the \textit{Journal of Hydrologic Engineering}, published by the American Society of Civil Engineers, and the \textit{Earth's Future}, published by the American Geophysical Union, for granting the rights to include their articles as part of this dissertation.
  % \par}
}